### 2019-02-14 README.Rmd
some find/replace

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# citesdb

@@

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)
[![CircleCI](https://circleci.com/gh/ecohealthalliance/citesdb.svg){data-external="1"}](https://circleci.com/gh/ecohealthalliance/citesdb)
  [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/ecohealthalliance/citesdb?branch=master&svg=true){data-external="1"}](https://ci.appveyor.com/project/ecohealthalliance/citesdb)
[![codecov](https://codecov.io/gh/ecohealthalliance/citesdb/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/ecohealthalliance/citesdb)
[![CRAN status](https://www.r-pkg.org/badges/version/monetpkg){data-external="1"}](https://cran.r-project.org/package=monetpkg)

@@

```{r version}
packageVersion("monetpkg")
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(dplyr)
```
# citesdb

@@

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)
[![CircleCI](https://circleci.com/gh/ecohealthalliance/citesdb.svg){data-external="1"}](https://circleci.com/gh/ecohealthalliance/citesdb)
  [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/ecohealthalliance/citesdb?branch=master&svg=true){data-external="1"}](https://ci.appveyor.com/project/ecohealthalliance/citesdb)
[![codecov](https://codecov.io/gh/ecohealthalliance/citesdb/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/ecohealthalliance/citesdb)
[![CRAN status](https://www.r-pkg.org/badges/version/citesdb){data-external="1"}](https://cran.r-project.org/package=citesdb)

@@

```{r version}
packageVersion("citesdb")
```
